\documentclass[11pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage[margin=0.75in]{geometry}
\usepackage{graphicx}
\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=linkblue,
    urlcolor=linkblue,
    citecolor=linkblue
}
\usepackage{xcolor}
\usepackage{fancyhdr}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{tcolorbox}
\usepackage{fontawesome5}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{lmodern}
\usepackage[T1]{fontenc}
\usepackage{needspace}
\usepackage{multicol}

% UC Davis Colors
\definecolor{ucdavisblue}{RGB}{0,78,146}
\definecolor{ucdavisgold}{RGB}{255,191,0}
\definecolor{ucdavisgolddark}{RGB}{204,153,0}
\definecolor{lightgray}{RGB}{248,249,250}
\definecolor{darkgray}{RGB}{75,85,99}
\definecolor{green}{RGB}{34,197,94}
\definecolor{linkblue}{RGB}{0,102,204}

% Header and footer
\setlength{\headheight}{15pt}
\addtolength{\topmargin}{-3pt}
\pagestyle{fancy}
\fancyhf{}
\fancyhead[L]{\textcolor{ucdavisblue}{\textbf{Mohammadreza Narimani - Curriculum Vitae}}}
\fancyhead[R]{\textcolor{ucdavisblue}{UC Davis}}
\fancyfoot[C]{\thepage}

% Title formatting
\titleformat{\section}{\Large\bfseries\color{ucdavisblue}}{}{0em}{}[\titlerule]
\titleformat{\subsection}{\large\bfseries\color{ucdavisblue}}{}{0em}{}
\titleformat{\subsubsection}{\normalsize\bfseries\color{darkgray}}{}{0em}{}

% Custom boxes
\newtcolorbox{contactbox}{
    colback=ucdavisgold!20,
    colframe=ucdavisblue,
    boxrule=2pt,
    arc=5pt,
    left=15pt,
    right=15pt,
    top=15pt,
    bottom=15pt
}

\newtcolorbox{skillbox}{
    colback=ucdavisblue!10,
    colframe=ucdavisblue,
    boxrule=1pt,
    arc=3pt,
    left=10pt,
    right=10pt,
    top=8pt,
    bottom=8pt
}

% Custom list styles
\setlist[itemize]{leftmargin=15pt, itemsep=3pt, parsep=2pt}
\setlist[enumerate]{leftmargin=15pt, itemsep=4pt, parsep=2pt}

\begin{document}
\sloppy

% Header Section
\begin{center}
    {\Huge\bfseries\color{ucdavisblue} Mohammadreza Narimani}\\[0.3cm]
    {\Large\color{darkgray} PhD Candidate in Biological Systems Engineering}\\[0.2cm]
    {\large\color{darkgray} University of California, Davis}\\[0.2cm]
    {\normalsize\color{darkgray} Biological and Agricultural Engineering Department}\\[0.2cm]
    {\normalsize\color{darkgray} California, US}\\[0.5cm]
\end{center}

\begin{contactbox}
\begin{center}
\begin{tabular}{ll}
\textbf{\faGlobe\ Website:} & \href{https://mohammadrezanarimaniucdavis.github.io/}{\underline{mohammadrezanarimaniucdavis.github.io}} \\
\textbf{\faGithub\ GitHub:} & \href{https://github.com/MohammadrezaNarimaniUCDavis}{\underline{MohammadrezaNarimaniUCDavis}} \\
\textbf{\faGraduationCap\ Scholar:} & \href{https://scholar.google.com/citations?user=BV95fNoAAAAJ}{\underline{Google Scholar Profile}} \\
\textbf{\faEnvelope\ Email:} & mnarimani@ucdavis.edu \\
\textbf{\faEnvelope\ Personal:} & narimanimohammadreza@gmail.com
\end{tabular}
\end{center}
\end{contactbox}

\vspace{0.3cm}

% Research Interests
\section{Research Interests}
Remote Sensing of Agriculture and Environment • Earth Observation • Digital Agriculture • Machine Learning • Computer Vision • Precision Agriculture • Hyperspectral Imaging • LiDAR • Satellite Data Analysis • IoT Systems • Plant Phenotyping • 3D Radiative Transfer Modeling • Wildfire Detection

% Education
\section{Education}

\subsection{\texorpdfstring{Ph.D. Candidate of Biological Systems Engineering \hfill 2022--Present}{Ph.D. Candidate of Biological Systems Engineering (2022--Present)}}
\textbf{University of California, Davis, US} \hfill \textcolor{ucdavisgolddark}{\textbf{GPA: 4.0/4.0}}\\
\textit{Thesis:} AI-Driven Remote Sensing and Spectral Modeling for Advanced Monitoring of Tomato Crops\\
\textit{Advisors:} Prof. Alireza Pourreza, Prof. Ali Moghimi

\subsection{\texorpdfstring{M.Sc. of Biosystem Mechanical Engineering \hfill 2019--2021}{M.Sc. of Biosystem Mechanical Engineering (2019--2021)}}
\textbf{University of Tehran, Iran} \hfill \textcolor{ucdavisgolddark}{\textbf{GPA: 4.0/4.0 (First Rank)}}\\
\textit{Thesis:} Designing and Manufacturing an Experimental Smart Greenhouse for High-Throughput Stress Phenotyping and Plant Disease Detection by Implementing Internet of Things System and Machine Learning

\subsection{\texorpdfstring{B.Sc. of Biosystem Mechanical Engineering \hfill 2015--2019}{B.Sc. of Biosystem Mechanical Engineering (2015--2019)}}
\textbf{University of Tehran, Iran} \hfill \textcolor{ucdavisgolddark}{\textbf{GPA: 4.0/4.0 (First Rank)}}\\
\textit{Thesis:} Design and construction of electric turning machine for urban agriculture

% Research Experience
\section{Research Experience}

\subsection{\texorpdfstring{Research Assistant \hfill 2022--Present}{Research Assistant (2022--Present)}}
\textbf{Digital Agriculture Laboratory, University of California, Davis}
\begin{itemize}
    \item AI-Driven Remote Sensing and Spectral Modeling for Advanced Monitoring of Tomato Crops
    \item 3D Radiative Transfer Modeling for Specialty Crops
    \item Wildfire Detection and Monitoring Using Satellite Imagery and Deep Learning
    \item Image semantic segmentation using FCN\_AlexNet, SegNet, and U-Net for Agricultural Vision Competition
\end{itemize}

\subsection{\texorpdfstring{Research Assistant \hfill 2016--2022}{Research Assistant (2016--2022)}}
\textbf{University of Tehran, Iran}
\begin{itemize}
    \item High-Throughput Wheat Phenotyping for Agricultural Research Institute of Iran, Wheat Species Bank
    \item Detecting fungal disease of lettuce with thermal camera and CNNs
    \item Image processing algorithms for measuring friction coefficient and angle of repose in rice grain
    \item IoT device development using Arduino, Raspberry Pi, Ethernet, and ESP8266
    \item Designing novel fogponic and centrifugal irrigation systems for aeroponic greenhouses
    \item Deep learning algorithms for detecting powdery tomato disease
    \item Designing strawberry harvester robot
\end{itemize}



\subsection{\texorpdfstring{Internship \hfill 2017--2022}{Internship (2017--2022)}}
\textbf{Agricultural Engineering Research Institute of Iran (AERI)}

% Skills
\section{Technical Skills}

\begin{skillbox}
\textbf{Remote Sensing Tools:} Sentinel-2, Landsat-9, EMIT, ECOSTRESS, DJI Phantom 4 Multispectral, Aerial Pika-L Hyperspectral Sensor, Aerial Phoenix LiDAR Systems
\end{skillbox}

\begin{skillbox}
\textbf{Programming Languages:} Python, R, MATLAB, C++
\end{skillbox}

\begin{skillbox}
\textbf{Amazon Web Services:} Lambda, S3, App Runner, API Gateway, EC2, Elastic Container Registry, IAM, CloudFormation, CloudWatch
\end{skillbox}

\begin{skillbox}
\textbf{Techniques:} Computer Vision, Image Processing, Deep Learning, Machine Learning, Web App Development, Internet of Things, Robotics
\end{skillbox}

\begin{skillbox}
\textbf{Prominent Libraries:} Keras, TensorFlow, PyTorch, scikit-learn, geemap, rasterio, gdal, pandas, NumPy, OpenCV, PlantCV, scikit-image
\end{skillbox}

\begin{skillbox}
\textbf{GIS:} ArcGIS, QGIS, Google Earth Engine, ENVI, Pix4D, Resonon, Spatial Explorer, Microstation, Terrasolid
\end{skillbox}

\begin{skillbox}
\textbf{Computer-Aided Design and Engineering:} CATIA, SolidWorks, AutoCAD, Abaqus, Ansys, Keyshot
\end{skillbox}

% Publications
\section{Journal Publications}

\begin{enumerate}
\item Farajpoor, P., Pourreza, A., \textbf{Narimani, M.R.}, El‐Kereamy, A., Fidelibus, M. (2025). Multi-Trait Spectral Modeling for Estimating Grapevine Leaf Traits and Nutrients. \textit{Plant Phenomics}. \href{https://www.sciencedirect.com/science/article/pii/S2643651525001487}{\underline{DOI Link}}

\item \textbf{Narimani, M.R.}, Pourreza, A., Moghimi, A., Farajpoor, P., Jafarbiglu, H., Mesgaran, B. (2025). Early Detection of Branched Broomrape (Phelipanche Ramosa) Infestation in Tomato Crops by Using Leaf Spectral Analysis and Machine Learning. \textit{IFAC-PapersOnLine}. \href{https://arxiv.org/abs/2509.12074}{\underline{arXiv Link}}

\item Alimardani, R., Adedeji, A.A., \textbf{Narimani, M.R.} (2025). A Review of IoT Applications in Food Processing and Related Fields. \textit{Journal of Food Processing and Preservation}. \href{https://onlinelibrary.wiley.com/doi/full/10.1155/jfpp/3064441}{\underline{DOI Link}}

\item \textbf{Narimani, M.R.}, Pourreza, A., Moghimi, A., Farajpoor, P., Jafarbiglu, H., Mesgaran, B. (2025). Branched broomrape detection in tomato farms using satellite imagery and time-series analysis. \textit{SPIE Defense + Commercial Sensing}. \href{https://doi.org/10.1117/12.3059998}{\underline{DOI Link}}

\item Farajpoor, P., Pourreza, A., \textbf{Narimani, M.R.}, El‐Kereamy, A., Fidelibus, M. (2024). Leaf spectral reflectance prediction using multihead attention neural networks. \textit{SPIE Defense + Commercial Sensing}. \href{https://doi.org/10.1117/12.3061298}{\underline{DOI Link}}

\item \textbf{Narimani, M.R.}, Pourreza, A., Moghimi, A., Mesgaran, B., Farajpoor, P., Jafarbiglu, H. (2024). Drone-based multispectral imaging and deep learning for timely detection of branched broomrape in tomato farms. \textit{SPIE Defense + Commercial Sensing}. \href{https://doi.org/10.1117/12.3021219}{\underline{DOI Link}}

\item Akpenpuun, T.D., Ogunlowo, Q.O., Na, W.H., Dutta, P., Rabiu, A., Adesanya, M.A., \textbf{Narimani, M.R.}, et al. (2024). Dynamic neural network modeling of thermal environments of two adjacent single-span greenhouses. \textit{Journal of Agricultural Engineering}. \href{https://doi.org/10.4081/jae.2024.1563}{\underline{DOI Link}}

\item \textbf{Narimani, M.R.}, Hajiahmad, A., Moghimi, A., Alimardani, R., Rafiee, S., Mirzabe, A.H. (2021). Developing an aeroponic smart experimental greenhouse for controlling irrigation and plant disease detection using deep learning and IoT. \textit{ASABE Journal}. \href{https://elibrary.asabe.org/abstract.asp?aid=52586}{\underline{Publication Link}}

\item Kianmehr, M., Elyasi, M., \textbf{Narimani, M.R.} Design and construction of electric turning machine for urban agriculture. \textit{Journal of Tarbiyat Modares University}. \href{https://civilica.com/doc/838593/}{\underline{Publication Link}}
\end{enumerate}

\section{Conference Presentations}

\begin{enumerate}
\item \textbf{Narimani, M.R.}, et al. (2025). Early Detection of Branched Broomrape Infestation in Tomato Crops. \textit{8th IFAC Conference on Sensing, Control and Automation Technologies for Agriculture}. \href{https://ifac.papercept.net/conferences/conferences/AGRI25/program/AGRI25_ContentListWeb_1.html\#weds2tb_03}{\underline{Conference Link}}

\item \textbf{Narimani, M.R.}, et al. (2024). Drone-based multispectral imaging and deep learning for timely detection of branched broomrape. \textit{SPIE Defense + Commercial Sensing}. \href{https://www.spiedigitallibrary.org/conference-proceedings-of-spie/13053/1305304/Drone-based-multispectral-imaging-and-deep-learning-for-timely-detection/10.1117/12.3021219.full}{\underline{Presentation Link}}

\item \textbf{Narimani, M.R.}, et al. (2024). Early Detection of Branched Broomrape in Tomato by Hyperspectral Sensing. \textit{ASABE 2024}.

\item Jafarbiglu, H., Pourreza, A., \textbf{Narimani, M.R.}, Sanden, B., Marino, G., Culumber, M., Mehata, M., Ferguson, L. (2024). Determining the best irrigation strategy for pistachio orchards with saline water and soil. \textit{SPIE Defense + Commercial Sensing}. \href{https://www.spiedigitallibrary.org/conference-proceedings-of-spie/PC13053/PC1305301/Determining-the-best-irrigation-strategy-for-pistachio-orchards-with-saline/10.1117/12.3021227.full}{\underline{Presentation Link}}

\item \textbf{Narimani, M.R.}, et al. (2024). Remote Sensing of Branched Broomrape in Tomato. \textit{65th Weed Day, UC Davis}. \href{https://wric.ucdavis.edu/events/weed_day_2024.html}{\underline{Event Link}}

\item \textbf{Narimani, M.R.}, et al. (2023). Wildfire Detection and Monitoring Using Satellite Imagery and Deep Learning. \textit{ASABE 2023}. \href{https://www.asabe.org/Portals/0/Events/2023\%20AIM/Tech.Schd.wPres.pdf}{\underline{Schedule Link}}

\item Jafarbiglu, H., Pourreza, A., \textbf{Narimani, M.R.}, Williams, D., Ferguson, L. (2023). Determining the best irrigation practices for pistachio orchards with saline water and soil. \textit{ASABE 2023}. \href{https://www.asabe.org/Portals/0/Events/2023\%20AIM/Tech.Schd.wPres.pdf}{\underline{Schedule Link}}

\item \textbf{Narimani, M.R.}, Hajiahmad, A., Moghimi, A., Alimardani, R., Rafiee, S., Mirzabe, A.H. (2021). Developing an aeroponic smart experimental greenhouse for controlling irrigation and plant disease detection using deep learning and IoT. \textit{ASABE 2021}.
\end{enumerate}

\section{Conference Posters}

\begin{enumerate}
\item \textbf{Narimani, M.R.}, Pourreza, A., Moghimi, A., Farajpoor, P., Jafarbiglu, H., Mesgaran, B. (2025). Branched broomrape detection in tomato farms using satellite imagery and time-series analysis. \textit{SPIE Defense + Commercial Sensing}. \href{https://www.spiedigitallibrary.org/conference-proceedings-of-spie/13475/134750V/Leaf-spectral-reflectance-prediction-using-multihead-attention-neural-networks/10.1117/12.3061298.short}{\underline{Poster Link}}

\item Jafarbiglu, H., Pourreza, A., \textbf{Narimani, M.R.}, Bailey, J., Taylor, G. (2024). Seam Carving for Tree Segmentation in Dense Tree Farms. \textit{ASABE 2024}.

\item \textbf{Narimani, M.R.}, Hajiahmad, A., Moghimi, A., Alimardani, R., Rafiee, S., Mirzabe, A.H. (2021). Developing an aeroponic smart experimental greenhouse for controlling irrigation and plant disease detection using deep learning and IoT. \textit{ASABE 2021}.
\end{enumerate}

% Teaching Experience
\section{Teaching Experience}

\noindent\textbf{Teaching Assistant, University of California, Davis} \hfill 2022--Present
\begin{itemize}
    \item Applied Statistics in Agricultural Sciences \href{https://mohammadrezanarimaniucdavis.github.io/PLS120-Statistics-Lab-Materials/}{\underline{Lab Materials}}
    \item Introduction to Unmanned Aerial Systems for Agriculture \& Environmental Science
    \item Communications and Computing Technology (IoT in Ag) \href{https://mohammadrezanarimaniucdavis.github.io/TAE30-IoT-Lab-Materials/}{\underline{Lab Materials}}
\end{itemize}

\noindent\textbf{Teaching Assistant, University of Tehran, Iran} \hfill 2016--2022
\begin{itemize}
    \item Programming with Python and MATLAB
    \item Computer Vision and Artificial Intelligence
    \item Industrial drawing with CATIA, SolidWorks and AutoCAD
\end{itemize}

\noindent\textbf{Teaching Physics, Bonyad Amoozeshi Ghalamchi} \hfill 2014--2016

% Awards and Honors
\section{Awards and Honors}

\begin{itemize}
    \item Future Undergraduate Science Educators (FUSE) Program Scholarship \hfill 2025--Present
    \item Best Presentation Award, ASABE Annual International Meeting \hfill 2024
    \item Agricultural Genome to Phenome Initiative Scholarship \hfill 2024
    \item Bill And Jane Fischer Vegetation Management Scholarship \hfill 2024
    \item Member of SPIE Defense + Commercial Sensing \hfill 2024--Present
    \item Peter J. Shields and Henry A. Jastro Research Award \hfill 2023
    \item Dean's Distinguished Graduate Fellowship \hfill 2022
    \item Member of ASABE (American Society of Agricultural and Biological Engineers) \hfill 2021--Present
    \item First rank prize, Iran IoT and Computer Vision Competition \hfill 2020
    \item Member of Iran Elite Foundation (Bonyad Melli Nokhbegan) \hfill 2017--2022
\end{itemize}

% Leadership and Service
\section{Leadership and Service}

\subsection{Leadership Positions}
\begin{itemize}
    \item Vice President, Graduate Student Association, BAE Department, UC Davis \hfill 2024--Present
    \item Representative, Graduate Student Association, BAE Department, UC Davis \hfill 2023--2024
    \item Election Committee Member, Graduate Student Association, BAE Department \hfill 2025
\end{itemize}

\subsection{Mentorship}
\begin{itemize}
    \item Mentor, E-SEARCH Program, UC Davis (4 undergraduate students) \hfill 2024--Present
    \item Mentor, AgTech Workshop (Drone \& IoT), AI Institute for Next Generation Food Systems \hfill 2023--Present
    \item Mentor, Young Scholar Program, UC Davis (high school students) \hfill 2023
\end{itemize}

\subsection{Mentees' Research Posters}
\begin{itemize}
    \item Sun, V.J., \textbf{Narimani, M.R.} Deep Learning-Based Snow Monitoring in California Using Sentinel-2 Satellite Data. \href{https://engineering.ucdavis.edu/e-search}{\underline{ESEARCH}} Summer 2025.
    \item Kumar, S., \textbf{Narimani, M.R.}, et al. Enhancing Orchard Management with Deep Learning: Tree Segmentation Using Geospatial SAM2 Model. \href{https://engineering.ucdavis.edu/e-search}{\underline{ESEARCH}} Fall 2024.
    \item Richmond, N., \textbf{Narimani, M.R.}, et al. Global Vegetation and Climate Insights Portal (GVCIP). \href{https://engineering.ucdavis.edu/e-search}{\underline{ESEARCH}} Summer 2024.
    \item Tran, Q., \textbf{Narimani, M.R.}, et al. Enhancing Wildfire Monitoring Through Remote Sensing. \href{https://engineering.ucdavis.edu/e-search}{\underline{ESEARCH}} Spring 2024.
\end{itemize}

\subsection{Editorial and Peer Review Activities}
\textbf{Reviewer for the following journals:} \hfill 2024--Present
\begin{itemize}
    \item Scientific Reports (Springer Nature)
    \item Journal of Agriculture and Food Research (Elsevier)
    \item Journal of Food Science (Wiley)
    \item Smart Agricultural Technology (Elsevier)
    \item Computers and Electronics in Agriculture (Elsevier)
    \item Information Processing in Agriculture (Elsevier)
    \item Remote Sensing Applications: Society and Environment (Elsevier)
    \item NJAS: Impact in Agricultural and Life Sciences (Taylor \& Francis)
\end{itemize}



% Media Coverage
\section{Media Coverage}

\textbf{Parasitic Weeds Threaten Tomato Plants on California Farms} - Featured in:
\begin{itemize}
    \item UC Davis Newsletter \href{https://www.ucdavis.edu/food/news/parasitic-weeds-threaten-tomato-plants-on-california-farms}{\underline{Read Article}}
    \item UC Davis College of Agricultural and Environmental Sciences \href{https://caes.ucdavis.edu/news/parasitic-weeds-threaten-tomato-plants-california-farms}{\underline{Read Article}}
    \item Daily Democrat Newspaper \href{https://www.dailydemocrat.com/2024/03/20/parasitic-weeds-threaten-tomato-plants-on-california-farms}{\underline{Read Article}}
    \item Ag Alert Magazine \href{https://california-farm-bureau-publications.cfbf.com/view/617470051/8}{\underline{Read Article}}
    \item Capital Press Newsletter \href{https://www.capitalpress.com/ag_sectors/research/the-enemy-underground-california-researchers-target-parasitic-weed/article_708c3668-613b-11ee-9e7f-137682d06e8c.html}{\underline{Read Article}}
    \item Organic Growers Newsletter \href{https://organicgrower.info/news/researchers-fight-weeds-threatening-california-tomatoes}{\underline{Read Article}}
    \item UC Davis Plant Sciences Newsletter \href{https://www.plantsciences.ucdavis.edu/news/parasitic-weeds-tomato-hanson}{\underline{Read Article}}
    \item Tomato News \href{https://www.tomatonews.com/en/broomrape-parasitic-weeds-threaten-california-tomato-fields_2_2117.html}{\underline{Read Article}}
    \item California Fruit and Vegetable \href{https://calfruitandveg.com/2024/04/29/read-2024-issue}{\underline{Read Article}}
\end{itemize}

\vfill

\begin{center}
\textit{Last updated: November 30, 2025}
\end{center}

\end{document}